Measuring precise radial velocities and cross-correlation function line-profile variations using a Skew Normal density\thanks{Based on observations collected at the La Silla Parana Observatory, ESO (Chile), with the HARPS spectrograph at the 3.6-m telescope.}

### 2018-11-14 manuscript_v2_noiseSim.tex
Add files via upload
updated sentences Sec.4 on comparison before/after correction

The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e. a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}. Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant. When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}}

@@

In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.}}
%This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.

>>>>

The RV variations displayed in Fig.~\ref{fig:faculae} are caused only by stellar activity, in this case a facula, so we applied the activity correction proposed in Eq.~\eqref{eq:RV:correction} to evaluate the performance of the model in this setting.
The results of this correction are displayed in Fig.~\ref{fig:faculae.correction} and the statistical tests on the coefficients involved in Eq.~\eqref{eq:RV:correction} are summarized in Table \ref{table:faculae.test}. 
The proposed correction for stellar activity is able to account for the majority of the activity signal created by a facula, with a {\bf{$R^2$ larger than $0.98$.}}
%In addition, the rms of the different estimates of the RV reduces from about {\bf{6 \ms}} before correcting for stellar activity to values below {\bf{1.2 \ms}} after correcting for stellar activity.
%We see a slightly smaller rms after correction when using the SN parameters compared to the Normal parameters.
{\bf{In addition the rms for N mean RV reduces from 8.02 \ms before correcting for stellar activity to about 1.2 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 7.07 \ms to 0.88 \ms and for SN mean RV are 5.9 \ms to 0.88 \ms.}}
When comparing the correction proposed in Eq.~\eqref{eq:RV:correction} with what is generally used (i.e. a linear combination of only the asymmetry and width parameters), we see that the proposed correction is able to reduce the rms of the RV residuals by  {\bf{15 \%}}. Looking at the significance of the coefficients in Table~\ref{table:faculae.test}, we observe that {\bf{all the parameters corresponding to the SN variables are statistically significant. When using the Normal variables, the parameters $\beta_{3}$ and $\beta_{4}$ are not statistically helpful for the correction.}}

@@

%In Fig.~\ref{fig:spot.correction}, we see that the proposed activity correction is able to reduce the signal of a spot from a raw RV rms larger than {\bf{6.14\ms}} down to a rms smaller than {\bf{3.05 \ms}}, for any of the different RV estimates.
{\bf{In addition the rms for N mean RV reduces from 6.14 \ms before correcting for stellar activity to about 3.04 \ms after once corrected for stellar activity using the proposed linear model; the respective values for SN median RV are 5.85 \ms to 2.74 \ms and for SN mean RV are 5.27 \ms to 2.74 \ms.}}
When comparing the activity correction proposed in this paper with what is commonly used, i.e only a linear combination of the width and asymmetry of the CCF, we see that our solution is capable of reducing the RV residual rms by {\bf{6 \%}}.
The Normal or SN parameters involved in Eq.~\eqref{eq:RV:correction} are all statistically significant to explain the activity signal as seen in Table~\ref{table:spot.test}, {\bf{except the width of the CCF and the variable that evaluates the interaction between the width and the asymmetry of the CCF.}}
%This is not surprising when looking at the circle shape drawn when plotting the width as a function of the RV in Fig.~\ref{fig:spot.corr}.
